Coherent optical association of a single molecule

### 2020-09-24 paper.tex
Update on Overleaf.

%The challenge of optical Raman association of molecules from atoms lies with achieving a high enough Raman Rabi frequency despite the wavefunction size mismatch between the atomic state and the excited molecular state. While pioneering experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
Therefore, finding the largest Raman Rabi frequency to scattering ratio that enables population transfer with minimal loss is the first key task.

@@

>>>>

%The challenge of optical Raman association of molecules from atoms lies with achieving a high enough Raman Rabi frequency despite the wavefunction size mismatch between the atomic state and the excited molecular state. While pioneering experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
%Therefore, finding the largest Raman Rabi frequency to scattering ratio that enables population transfer with minimal loss is the first key task.

@@

Pioneering experiments used weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency, but such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.
